%!TEX root = ../dissertation.tex
% the abstract

Computer Vision and Natural Language Processing are two of the most important applications of modern Artificial Intelligence. While problems on both areas have shown a great progress during recent years thanks to the introduction of Neural and Deep Learning models, there has been a reduced number of published works referred to the relation between language and vision. The method presented on this thesis aims to relate both types of inputs by solving the problem of object segmentation based on referring natural language queries.

The first part of this dissertation introduces a novel Deep Learning model that merges both visual and language information in a recurrent fashion by fusing Language Features, such as Word Embeddings and higher-dimensional representations obtained by training a Recurrent Neural model over the referring expression with low resolution visual convolutional features extracted by means of a Convolutional Neural Network (CNN) on the channel dimension of the latter one. As a novel contribution, the model takes into account a set of filters derived directly from the expression, whose convolutional response is directly related to different image features, such as spatial localization and color references that reinforce and improve the overall method performance accuracy. Finally, the upsampling step from low resolution to high resolution of the combined features takes advantage of the multiple resolution feature maps generated by the CNN. During this section, the proposed method is compared with the state-of-the-art approaches in four standard datasets, in which it yields high performance and surpasses all previous methods in six of eight of the standard dataset splits for this task.    

The second part of the tesis consists on the description, implementation and deployment of a mobile application that allows to take real-world images and process them using custom-user queries. The main objective of this component is not only to demonstrate the performance of the model in the wild, but also to present an application of the task, in this case by sorting and filtering images by means of a complex query, instead of using simple object tags.  

