%!TEX root = ../dissertation.tex
% the acknowledgments section

\newthought{I would like to acknowledge and give thanks} to Pablo in the first place, for believing in my work and helping me to reconnect with my passion for Computer Vision, Neural Nets and Deep Learning in general. I would like to thank him also for giving me the opportunity of take part of the Biomedical Computer Vision group where we admire his work and advices. Without them, I don't know what I would do with my future academic roadmap. This is also for Juan Camilo and Emilio, my partners on crime all these months on the way up of taking this project to ECCV. Most of the credits go to them, as the method presented on this thesis was not \textbf{definitely} an individual effort and it forms part of a bigger project.

On the second place, I would like to thank José Tiberio, for believing on this endeavour and giving me support with all the paperwork and formalities required at the Systems and Computing Engineering Department (Even when they were on the wrong schedule) and his personal advices. Also, I would like to thank him specially for giving me the opportunity of traveling to Kaiserslautern on Germany, where I did not only grew academically, but also as a person and a human being. I would like also to mention all the people that I met there and helped me to endure the winter, Klaus, Diana, Carol, Meili, Sergio, Ritu and Eda.

My thanks also go to Mario Linares, for guiding me and giving me advice on the mobile app development. Thank you for volunteering with this project and providing extra perspectives.

As this was a long process that took 4 years, I would like to thank hugely all of my closest friends that did support me throughout all this time, thanks for your love, time, patience and humor: 

Camila (''Llami'') for all those years of great teamwork and friendship, even at 3:00am sometimes or some semesters of waiting in-between. Thanks, thanks a lot for all the things that we did learn. We are flying far away, and I am very proud of it!

Stephannie (''Tefa'') and Sergio (''Checho''), for helping me to discover that I am somewhat of a Biomedical Engineering and also that I am Edgar \textit{et al.}, because I am never alone.

Diana (''Tostada'') for teaching me that all roads will take you to CS, even coming from Economics.

Daniella (''Hermana''), Carolina and for all the other people that did helped me and I could not mention here, this is also for you.

Finally, I would like to thank my family for all their support, to my mother and all her academical and life advices, to my father for taking care of everyday logistics and ensuring that I was always at time. To Ale and Héctor, for giving me light during those dark nights and reminding me that I am more than my fears, insecurities and masks.

%\newthought{Lorem ipsum dolor sit amet}, consectetuer adipiscing elit. Morbi commodo, ipsum sed pharetra gravida, orci magna rhoncus neque, id pulvinar odio lorem non turpis. Nullam sit amet enim. Suspendisse id velit vitae ligula volutpat condimentum. Aliquam erat volutpat. Sed quis velit. Nulla facilisi. Nulla libero. Vivamus pharetra posuere sapien. Nam consectetuer. Sed aliquam, nunc eget euismod ullamcorper, lectus nunc ullamcorper orci, fermentum bibendum enim nibh eget ipsum. Donec porttitor ligula eu dolor. Maecenas vitae nulla consequat libero cursus venenatis. Nam magna enim, accumsan eu, blandit sed, blandit a, eros.
